Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-11-13 lloveras_2020.tex
agregando midpoints

\section{Methodology}\label{meto}   
\subsection{DEMT reconstructions}\label{demt} 
\subsection{AWSoM simulations}\label{awsom} 
\subsection{Tracing results along fieldlines}\label{trace}

@@

B) Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green). This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.

@@

\subsection{Tomography and Models}\label{awsom_res} 
Same as A but for AWSoM model.
Same as B but for AWSoM model

>>>>

\section{Methodology}\label{meto}

\subsection{DEMT reconstructions}\label{demt}

\subsection{AWSoM simulations}\label{awsom}

\subsection{Tracing results along fieldlines}\label{trace}

@@

B)    I - Small-closed field lines. Small meaning with apex within the DEMT range of heights. This class thoroughly probes the inner core of the Streamer belt, where most of the DOWN loops showed up before, and will show up now.

  II - Large-closed field lines. Large meaning their apex surpasses the DEMT range of heights. This class is mostly populated by very large trans-equatorial field lines forming the "envelope" of the Streamer belt.

 III - Open field lines.

Carrington maps of the Lat/Lon location at 1.105 Rs of the field lines I (in blue), II (in red), and III (in green). This shows in a very graphical way which regions of the corona are probed by the three classes of selected field lines.

\begin{figure}%[h]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_demt_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_awsom_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_demt_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Latitude-longitude location of field lines meeting the criteria listed in Section \ref{trace} traced with DEMT results, at heights $1.105\,\mrsun$, for CR-2082(left panel) and CR-2208 (right panel). Different colors identify diverse thermodynamical and magnetic structures, as described in the text.}
\label{rpoint}
\end{center}
\end{figure}

@@

\subsection{Tomography and Models}\label{awsom_res}

\begin{figure}%[h]
\begin{center}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2082_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2082_awsom_paper_Rpoint-map.eps}
%\includegraphics[width=0.495\textwidth,clip=]{Highpoint_2208_demt_paper_Rpoint-map.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/Highpoint_2208_awsom_paper_Rpoint-map.eps}
\caption{Same as \ref{rpoint_demt} but for AWSoM loops.}
\label{rpoint_awsom}
\end{center}
\end{figure}
